---
title: "SRT411A0.Rmd"
author: "Eric Leung"
date: "March 22, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
ToDo

3.1
```{r}
(2018 - 2014) / (2014-1997) * 100
```
3.2
```{r}
a=4
b=(2014-1997)
a/b*100
```
3.4
```{r}
sum(4,5,8,11)
```
3.5
```{r}
u=rnorm(100)
plot(u)
```
4
```{r}
help(sqrt)
```
5
```{r}
source("firstscript.R")
```
6.2
```{r}
p=seq(from=31, to=60, by=1)
q=matrix(data=p,ncol=5,nrow=6)
q
```
6.3
this just plots a bunch of random number between -3 and +5
```{r}
x1=c(rnorm(100))
x2=c(rnorm(100))
x3=c(rnorm(100))
t=data.frame(a=x1,b=x1+x2,c=x1+x2+x3)
plot(t)
```
7
the rgb represents the color of whatever the arguemnt is plotting, in this case
it could be the plot, the lines, and the points that have a specific colour

lwd seems like it controls the width/thickness of whatever the argument it is 
describing, if you increase the lwd, the width/size of the line increases
 
pch seems to change the shape of the points depending on the value and cex changes
the overall size of the points depending on the value, the higher the bigger.
```{r}
plot(t$a, type="l", ylim=range(t),
     lwd=3, col=rgb(1,0,0,0.3))
lines(t$b, type="s", lwd=2,
      col=rgb(0.3,0.4,0.3,0.9))
points(t$c, pch=20, cex=4,
       col=rgb(0,0,1,0.3))
```
8
```{r}
d1=read.table(file="tst1.txt",header=TRUE)
d2=d1$g*5
write.table(d2,file="tst2.txt",row.names=FALSE,col.names="g")
```
9
```{r}
d3=data.frame=c(1:100,1)
d3^2

```
10.2
```{r}
date1=strptime(c("20140706080000","20150706000000"),format="%Y%m%d%H%M%S")
present=c(10,6)
date1
present
```
11.2
```{r}
v=seq(from=1, to=100, by=1)
s=c()
for(i in 1:100)
{
  if(v[i]<5)
  {
    s[i]=v[i]*5;
  }
  else if(v[i]>90)
  {
    s[i]=v[i]*10;
  }
  else
  {
    s[i]=v[i]*0.1;
  }
}
s
```
11.3
```{r}
f=function(arg1,arg2)
{
  v[i]=arg1[i];
  for(i in length(v))
  {
    
  }
}
f
```












